Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-08-04 paper/paperv1.0.tex
Python3->Python 3, two typos.

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:nvt_harmonic},
caption={MC simulation of a single particle in one dimension attached to a harmonic spring using Python3, where the statistics module is provided in Section~\ref{sec:block_av}. Note that a random number generator seed of "43279857" is provided so that the simulation is reproducible.}
]{../codes/nvt_harmonic.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_npt},
caption={MC simulation of an ideal gas in the $NPT$ ensemble using Python3 with a shell particle and uniform changes in $V$ or $\ln V$, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_npt.py}
\end{figure}

@@

Thus, the acceptance probability for deletions is given by
\begin{equation}
\chi = \frac{P_{\omega o} N_i}{Vz_i}e^{-\beta\Delta U},
\label{eq:lhs_del}
\end{equation}
where $P_{\omega o}=1$ (or incorporated into the definition of $z_i$) if rigid bodies are inserted with random orientations (using quaternsions, as discussed in Section~\ref{sec:lhs_rotation} and \ref{sec:unit_sphere}), or otherwise related to the Rosenbluth factor in CB \cite{frenkel_understanding_2002}.
Code Block~\ref{sim:ideal_gas_muvt} uses Eqs.~\ref{eq:lhs_ins} and \ref{eq:lhs_del} for an ideal gas to compare against theory, Eq.~\ref{eq:gce_ideal_gas_density}.

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_muvt},
caption={MC $\mu VT$ simulation of an ideal gas using Python3, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_muvt.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_sgcmc},
caption={Semi-$\mu VT$ MC of a two component ideal gas mixture using Python3, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_sgcmc.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_sgcmc_alt},
caption={Alternative algorithm for semi-$\mu VT$ MC of an ideal gas mixture using Python3, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_sgcmc_alt.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:gibbs_particle},
caption={MC simulation of an ideal gas in the Gibbs ensemble with chemical equilibrium using Python3 should yield two domains with equivalent density, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_gibbs_particle.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:gibbs_volume},
caption={MC simulation of an ideal gas in the Gibbs ensemble with mechanical equilibrium using Python3 should yeild two domains with equivalent density, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_gibbs_volume.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:gibbs},
caption={MC simulation of an ideal gas in the Gibbs ensemble with mechanical and chemical equilibrium using Python3 should yield two domains with equivalent number of particles and volume.}
]{../codes/ideal_gas_gibbs.py}
\end{figure}

>>>>

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:nvt_harmonic},
caption={MC simulation of a single particle in one dimension attached to a harmonic spring using Python 3, where the statistics module is provided in Section~\ref{sec:block_av}. Note that a random number generator seed of "43279857" is provided so that the simulation is reproducible.}
]{../codes/nvt_harmonic.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_npt},
caption={MC simulation of an ideal gas in the $NPT$ ensemble using Python 3 with a shell particle and uniform changes in $V$ or $\ln V$, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_npt.py}
\end{figure}

@@

Thus, the acceptance probability for deletions is given by
\begin{equation}
\chi = \frac{P_{\omega o} N_i}{Vz_i}e^{-\beta\Delta U},
\label{eq:lhs_del}
\end{equation}
where $P_{\omega o}=1$ (or incorporated into the definition of $z_i$) if rigid bodies are inserted with random orientations (using quaternions, as discussed in Section~\ref{sec:lhs_rotation} and \ref{sec:unit_sphere}), or otherwise related to the Rosenbluth factor in CB \cite{frenkel_understanding_2002}.
Code Block~\ref{sim:ideal_gas_muvt} uses Eqs.~\ref{eq:lhs_ins} and \ref{eq:lhs_del} for an ideal gas to compare against theory, Eq.~\ref{eq:gce_ideal_gas_density}.

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_muvt},
caption={MC $\mu VT$ simulation of an ideal gas using Python 3, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_muvt.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_sgcmc},
caption={Semi-$\mu VT$ MC of a two component ideal gas mixture using Python 3, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_sgcmc.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:ideal_gas_sgcmc_alt},
caption={Alternative algorithm for semi-$\mu VT$ MC of an ideal gas mixture using Python 3, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_sgcmc_alt.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:gibbs_particle},
caption={MC simulation of an ideal gas in the Gibbs ensemble with chemical equilibrium using Python 3 should yield two domains with equivalent density, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_gibbs_particle.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:gibbs_volume},
caption={MC simulation of an ideal gas in the Gibbs ensemble with mechanical equilibrium using Python 3 should yield two domains with equivalent density, and the statistics module is provided in Section~\ref{sec:block_av}.}
]{../codes/ideal_gas_gibbs_volume.py}
\end{figure}

@@

\begin{figure}
\lstinputlisting[
language=Python,
label={sim:gibbs},
caption={MC simulation of an ideal gas in the Gibbs ensemble with mechanical and chemical equilibrium using Python 3 should yield two domains with equivalent number of particles and volume.}
]{../codes/ideal_gas_gibbs.py}
\end{figure}
